Unsupervised Acquisition of Comprehensive Multiword Lexicons \\ using Competition in an $n$-gram Lattice

### 2017-05-23 reviewer_response.txt

We would like to thank all of our reviewers for their detailed comments. We have tried to address the important points as best we can, but we were limited to provided with 3 extra pages (beyond the 10 pages of the original submission), and because all the reviews had numerous suggestions for improvement with only one obvious overlaps, we have had to pick and choose what we could add. In cases where we did not change the paper, threre is a justification below.

@@

>In the introduction, the proposed approach is claimed to be "effective,
expandable, and tractable", however, it is not clear how each of these
claims is evaluated in the paper (effective, expandable and tractable). The
approach is also claimed to have the candidates compete for "the best (most
parsimonious) explanation for statistical irregularities due to lexical
affinity", but concepts like parsimony and lexical affinity need to be
defined (what are they, how candidates display them, and how they are
measured, ...).

Our intent is that effectiveness is demonstrated by our main evaluation. Tractability is demonstrated implicitly by the fact that we apply our method to corpora much larger than many of our competitors can handle. We have added more details about this to the paper, though we do not want to belabour the point, since it is not the primary purpose. Our claim of expandability relates to our discussion of future work, however we have added a bit more discussion about exactly how expansions would be added without major changes to the model.

> The paper should explicitly state what the hypotheses are in relation to the
utility functions, particularly in relation to the approach by Brooke et al.
(2015), which is simpler than the proposed approach. Moreover, the
state-of-the-art has several simpler formulations for the identification of
general formulaic sequences of flexible sizes (e.g. Silva et al. 1999 for
contiguous & non-contiguous cases and Villavicencio et al. 2007 for
contiguous cases), and the text should justify why this particular approach
is appealing, and advantageous in relation to the others. The addition of an
error analysis would help highligh these points, helping to clarify the
advantages of the particular approach especially in relation to Brooke et
al.

We have added a new paragraph contrasting our method to other algorithms, and an qualitative discussion which doubles as an error analysis.

@@

>The paper should also discuss the motivation for each of the node
interaction functions for rewarding/penalizing competitive candidates in the
lattice, including how they are expected to contribute to the overall
performance of the approach and if the authors considered alternative
functions or why these in particular, which linguistic intuition they wanted
to capture, why define E0 in terms of the minLPR and E1 of a cost parameter,
why they are introduced in the explainedness as exponents (why not using a
linear dependence, for example. A suggestion for helping the presentation is
for the authors to rewrite E0 and E1 into a single formula that combines the
three measures in a utility function, as it would be easier to explain (how
E0 and E1 compete, under which circumstances each of them wins),
particularly with the  addition of an example. In addition, when
presentating these functions, one problem is that although d0 and d1 are
used to define E0 and E1 in section 3.2, they are only defined in later
sections (sections 3.3.2 and 3.3.3). As a result the discussion appears too
abstract as the functions have not been completely defined yet. There should
be some explanation for their motivation/intuition, as it's not clear what
they are trying to capture, how E0 and E1 would vary for FS and non-FS, etc.
My suggestion is to first introduce and motivate the ideas behind them, and
later define them together. For d1, there is also a difference in the number
of arguments of "oc" in the text (oc(x,y)) and in the definition of d1
(oc(oi)). d0 is defined as a uniform combination of clear and cover, but it
would be helpful to have a discussion of the effects of different weights
for each of them for the different languages.

We have reorganized the presentation of the model and are now providing an explicit objective function, at the same time getting rid of the confusing forward pointers and many of the extra symbols.

We hope that the general purpose of each interaction in terms of the way that it inhibits other nodes is clear. We have added a bit more detail about the choice of the clearing function to both that section as well as the discussion.

@@

> * "has been turned on, the covering, blocking, or overlap- ping effects of
these other nodes" --> blocking shoud be clearing

Yes, thanks.

> * For the efficiency restrictions explain if other values have been tested
for them. How did they affect the overall performance? A table detailing the
behavior with different values would be helpful.

We've added a bit more detail, though perhaps not as much as you're asking for.

@@

Note that we are not ourselves proposing FS, we are borrowing the theory behind FS from the work of Wray (2002;2008), who includes an extremely thorough discussion of its relationship to other linguistic theories (Chapter 7 of the 2008
book in particular), including Construction Grammar. We have added a bit more detail to our introduction of FS to make it clear that, yes, most "constructions" are FS, and we have added constructions to Figure 1. However, ultimately
this is a technical paper, and we are limited in the space we can dedicate to theoretical concerns.

> The case of morphology is far less clear, however it is equally important,
and it has to do with the basic question of what is the unit that constructs
the FS (or the lattices themselves in empirical terms). Are these words?
morphemes? lemmas? POS? inflections? In the case  of words, what is the
relation of inflected sequences forms / inflected idioms (kicked his bucket
vs kicked her bucket, for instance) -- are they the same? related?
overalapping? subsumed?. As it stands, the discussion of morphology comes
out only later as an afterthought -- where the construction of the lattice
in Japanese (in the evaluation section) involves some morphological
segmentation whereas the lattice construction for the other languages
doesn't. It is thus unclear if the algorithm finds sequences that are of the
same type, or are comparable for that matter, across those languages. The
selected FS may be incomparable in terms of effective length (morpheme
sequences tend to be longer), the status of function words vs. inflection in
FS, and so on. The authors should put forth clearly what is the status of
morphology inside their general theory (and in terms of their regular
expressions), and then later revisit the empirical ramifications of their
decision -- for instance what happens when moving between typologically
different languages.

We have added a bit more to both the introduction of FS as well as a paragraph in the discussion that addresses this point. Ultimately, in all three languages we are tokenizing and lemmatizing using standards for each language, and building our FS from the result. However, this is not a theoretical choice, but a practical one.  With Japanese, due to the lack of word boundaries, morphological segmentation is a more standard form of tokenization, and so we have taken advantage of this to bring Japanese somewhat closer to our theoretical ideal. Given that many of the case markers of Japanese correspond to prepositions in European languages (or the possesive marker in English), the actual difference in generated FS is fairly minor, except for the extra overhead of word segmentation in Japanese that is provided by word boundaries in English (in Wray's theory, most words would be FS by default).

@@

Reviewer C:

> Where I had trouble was with the details of the model. First of all, much ofit seemed to be ad hoc; even accepting the notion of LPR from prior work,
there are many heuristic (or at least not obviously natural) choices made to
operationalize the general lattice idea mathematically. Second, even if the
model is reasonable, it is not entirely clear how the different parts fit
together into an optimization problem. There is mention of a parameter C;
and there is a notion of nodes being activated or not (I don’t think
notation is introduced for these binary variables, though it would be
appropriate). Are these the only things that have to be tuned? Is the
calculation of explainedness deterministic based on these? There is a greedy
search to optimize explainedness of the nodes in the lattice, subject to
various heuristics. Presenting a formal algorithm for the optimization may
clarify things considerably.

We have reorganized the method section and added an explicit objective function, which should help with some of your problems. In terms of the central optimization problem, the only variables are exactly the on/off status of each node, and, if we exclude the parameters used in the creation of the lattice (e.g. the n-gram frequency threshold) and those involved in the efficiency restrictions, the only (hyper)parameter in the optimization is C; we have a included psuedocode for optimization algorithm. With regards to the ad hoc parts of the model, we have added a discussion separating the core aspects of the model from some of the more ad hoc choices made in the particular instantions of component functions (such as clearing), making it clear that we believe these can potentially be improved on (both in terms of performance as well as mathematical elegance), and that our primary purpose here is to show that overall architecture of the model is a promising one.

@@

> I think it would also be worth discussing how the lattice model relates back to the cognitive/psychological literature. Would you predict (or are you
aware of any evidence) that node interactions such as covering, clearing,
and overlapping have an analogue in human language processing? Do any of the
design decisions intentionally sacrifice cognitive plausibility for
engineering reasons?

In general, we did not consider cognitive plausibility when creating the model, and we are certainly making no claims as such. For starters, our model makes use of more data than a human being could possibly read in a lifetime, it is clear humans identify FS with far less evidence than our model requires. With space, we could discuss our model in the context of the more cognative aspects of the theory of formulaic sequences as proposed by Wray, but given that this wasn't a focus in the development of the model, we think it is really too much of a digression to justify.

@@

>- Inter-annotator agreement is surprisingly high. Could you elaborate on
Wray’s criteria for FS that were applied by annotators?

Your surprise about the the Kappa being high is based on a misunderstanding: the kappa number reported in the table is after filtering to remove borderline cases (i.e. it is the kappa for the final test set, not the original sampling). To avoid confusion, we've added the original kappa score which is quite a bit lower. Your intution is correct that there is significant subjectivity to FS identification (more so than MWE annotation), and as such we would never rely on a single annotator for building a FS test set. We have not added more information about Wray's criteria; though it provide a starting point for annotation, more relevant to achieving reasonable agreement are the specific annotation guidelines which we created. Presenting them in the paper would be too much of a digression, but we promise to make them public.

> - I would like to see qualitative analysis of the sequences that were
identified as formulaic (or not) by annotators/the method. E.g.: How many of
them are syntactic constituents? Are there a wide variety of grammatical
kinds of expressions? Are high-frequency as well as low-frequency sequences
detected? What is the distribution in terms of length? What kinds of gapped
sequences are there? It would be nice to see some examples.

In the discussion, we have added a thorough analysis of specific examples and some statistics, including most of the information you ask for (implicitly if not explicitly).

@@

> - Related to the previous point: While noting the distinction between FS and
MWEs, is it perhaps worth measuring recall against MWE datasets? Most MWEs
apart from proper names should count as FS, right?

Do you mean as a way of evaluating different systems built on the same corpus, or just to get a sense of coverage more generally? One central problem with using recall for evaluation is that in order to make it fair, there must be some control of the size of the lexicon. Neither our system nor our best performing competitors are ranking models, none of them offer an easy or fair way to simply take the best N words and look at recall. And even if they did, there's other kinds of biases that would come into play: for instance, PMI and similar metrics do well with rare terms that correspond well to the MWE lexicon of WordNet, for instance, which (at the type level) is dominated by certain kinds of terminology (biomedical terms, particularly) which are not really used outside a very specific community. This relates to a more fundamental problem with the idea of using recall in external lexicons as any kind of useful measure: we could not expect any particular corpus (even a very large one) to do justice to the full range of FS/MWE for a language, since most of which appear regularly only within specific genres. For example, we could not expect to build a good lexicon of English verb-particle constructions from a biomedical corpus, because many are too informal to be appropriate for that genre (e.g. "mess up"). We have added more discussion of the corpus-specificity of FS to the paper, as part of the qualitative analysis.

Though it perhaps does not directly address your comment (since it doesn't involve an external MWE dataset), we were nonetheless inspired by your comment to include an analysis of the recall of MWE vs. non-MWE FS in the context of our existing test sets.

### 2017-05-23 tacl.tex

\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper]{geometry}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{url}
\usepackage{xspace}
\usepackage{paralist}
\usepackage{booktabs}
\usepackage[pdftex]{graphicx}
\usepackage{algorithm,algorithmicx}
\usepackage[noend]{algpseudocode}
\makeatletter
\newcommand{\@BIBLABEL}{\@emptybiblabel}
\newcommand{\@emptybiblabel}[1]{}
\makeatother
\usepackage[hidelinks]{hyperref}
\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{6.5cm}    % Expanding the titlebox

@@

\newcommand{\figref}[2][]{Figure#1~\ref{#2}\xspace}
\newcommand{\tabref}[2][]{Table#1~\ref{#2}\xspace}
\newcommand{\secref}[2][]{Section#1~\ref{#2}\xspace}
\newcommand{\algref}[2][]{Algorithm#1~\ref{#2}\xspace}

@@

A simple but effective solution which avoids introducing extra hyperparameters is to make use of the minLPR values of the relevant nodes. In the most common two-node situation, we increase the explainedness of the cleared node based on the ratio of the minLPR of two nodes, though only if the minLPR of the lower node is higher. Generalized to the (rare) case of multiple clearing nodes, we define $\clear(t)$ as:
%in this paper, we consider two options: a hard clearing where any turned-on node will clear (set $C_{0}$ to 0 for) any node higher in the lattice which has a minLPR that is lower than it; and a soft 
\begin{displaymath}
\clear(t) = \prod_{i=1}^{m}{\min\Big(1,\frac{\minLPR(t)}{\minLPR(u_i)}\Big)}
\end{displaymath}
where $u_i$ is the $i$th clearing node of $t$, \ie turned-on nodes below $t$ in the lattice. We refer to this mechanism as ``clearing'' because it tends to clear away a variety of trivial uses of common FS which may have higher LPR due to the lexical and syntactic specificity of the FS. For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, $\clear(t)$ will be 0.5. Like \cover, \clear takes on values in the range 0 to 1, with 1 being the default when no clearing occurs.

@@

\begin{algorithm}
	\caption{Optimization algorithm. $N$ is an ordered list of the nodes in the lattice. Nodes (designated by $n$) contain pointers to the nodes immediately linked to them the lattice. States (designated by $s$) indicate whether each node is $ON$ or $OFF$. Explainedness values are indicated by $e$.}
	\label{alg:opt}
	\begin{algorithmic}

	\Function{LocalOpt}{$s_{start}, n, N_{rev}, N_{af\hspace{-0.1em}f}$}
		\State $s_{start} \gets \Call{SetNode}{s, n, ON}$
		\State $Q \gets \Call{EmptyQueue}{\null}$
		\State $e_{best} \gets 0$
		\State $s_{best} \gets NULL$
		\State \Call{Push}{Q,$s_{start}$}
		\Repeat
			\State $s_{curr} \gets \Call{Pop}{Q}$
			\State $e_{curr} \gets \Call{CalcExpl}{s_{curr}, N_{af\hspace{-0.1em}f}}$
			\For{$n_{rev} \textrm{ in } N_{rev}$}
					\State $s_{new} \gets \Call{SetNode}{s_{curr}, OFF}$
					\State $e_{new} \gets\Call{CalcExpl}{s_{new}, N_{af\hspace{-0.1em}f}}$
					\If{$ e_{new} > e_{curr}$}

					\State \Call{Push}{$Q, s_{new}$}
					\If{$e_{new} > e_{best}}$:
							\State $e_{best} \gets e_{new}$
							\State $s_{best} \gets s_{new}$
					\EndIf
					\EndIf
				\EndFor
		\Until{\Call{IsEmpty}{Q}}
	\State \Return $s_{best}$
	\EndFunction
\State
\State \Call{FrequencySortReverse}{$N$}
\State $s \gets \Call{InitializeAllOff}{N}$
\Repeat
	\State $Changed \gets FALSE$
		\For{$n \textrm{ in } N$}
		\State $N_{rev} \gets \Call{GetRelevant}{n,N}$
		\State $N_{af\hspace{-0.1em}f} \gets \Call{GetAffected}{N_{rev},N}$
		\State $s_{new} \gets \Call{LocalOpt}{s,n,N_{rev},N_{af\hspace{-0.1em}f}}$
		\If{$s_{new} \neq s$}
			\State $s \gets s_{new}$
			\State $Changed \gets TRUE$
		\EndIf
		\EndFor
\Until{$!Changed$}
\State \Return $s$

@@

The dependence of the explainedness of nodes on their neighbors effectively prohibits a global optimization of the lattice. Fortunately, though most of the nodes in the lattice are part of a single main connected component, most of the effects of nodes on each other are relatively local, and effective local optimizations can be made tractable by applying some simple restrictions. The main optimization loop consists of iterations over the lattice until complete convergence (no changes in the final iteration). For each iteration over the main loop, each potentially active node is examined in order to evaluate whether its current status is optimal given the current state of the lattice. The order that we perform this has an effect on the result: among the obvious options, good results are obtained through ordering nodes by frequency, which gives an implicit advantage to relatively common $n$-grams.

Given the relationships between nodes, it is obviously not sufficient to consider switching only the present node. If, for instance, one or more of \ex{be keep \gap under wraps}, \ex{under wraps}, or \ex{be keep \gap under} has been turned on, the covering, clearing, or overlapping effects of these other nodes will likely prevent a competing node like \ex{keep \gap under wraps} from being correctly activated. Instead, the algorithm identifies a small set of ``relevant'' nodes which are the most important to the status of the node under consideration. Since turned-off nodes have no direct effect on each other, only turned-on nodes above, below, or overlapping with the current node in the Lattice need be considered.  Once the relevant nodes have been identified, all nodes (including turned-off nodes) whose explainedness is affected by one or more of the relevant nodes are identified. Next, a search is carried out for the optimal configuration of the relevant nodes, starting from an `all-on' state and then iteratively considering new states with one relevant node turned off; the search continues as long as there is an improvement in explainedness. Since the node interactions are roughly cumulative in their effects, this approach will generally identify the optimal state without the need for an exhaustive search. The details of the algorithm are given as Algorithm 1.%\algref{alg:opt}.

@@

	Lattice \emph{$-$cl$-$ovr} & 0.47& \bf{0.53} & 0.50 & & 0.31& \bf{0.60} & 0.41 & & 0.32 & 0.66 & 0.43 & & 0.49 & 0.61 & 0.54 \\

	Lattice \emph{$-$cl} & 0.57& 0.42 & 0.49 & & 0.33& 0.58 & 0.42 & & 0.39 & 0.56 & 0.46 & & 0.63 & 0.49 & 0.55 \\

	Lattice \emph{$-$ovr} & 0.52& 0.51 & 0.51 & & 0.34& \bf{0.60} & 0.44& & 0.36 & \bf{0.67} & 0.47 & & 0.53 & \bf{0.62} & 0.58 \\

@@

The main results for FS acquisition across all four corpora are shown in \tabref{tab:main}. As noted in previous work, simple statistical association measures like PMI do fairly poorly when faced with syntactically-unrestricted $n$-grams of variable length: minLPR is clearly a much better statistic for this purpose. The LPRseg method of \newcite{Brooke15b} consistently outperforms simple ranking, and the lattice method proposed here does better still, with a margin that is fairly consistent across languages. Generally, clearing and overlap node interactions provide a relatively large increase in precision at the cost of a smaller drop in recall, though the change is fairly symmetrical in Croatian. The Japanese and ICWSM corpus had relatively high precision and low recall, whereas both the BNC and Croatian corpus have low precision and high recall.

@@

Though the results across the four corpora are reasonably similar with respect to overall F-score, there are significant discrepancies. By using the UNIDIC morpheme representation as the base unit for Japanese, the model is doing an extra layer of FS identification, one which is provided by word boundaries in the other languages. The result is that there are many more FS for Japanese: precision is high, and recall is relatively low.  Importantly, the initial $n$-gram statistics derived from corpus reflect that Japanese is different: the number of $n$-gram types over length 4 is almost twice the number in the ICWSM corpus. One idea for future work is to automatically adapt to the input language/corpus in order to ensure a good balance between precision and recall.

At the opposite extreme, the low precision of the BNC is almost certainly at least somewhat a reflection of its relatively small size: whereas the $n$-gram threshold we have used here results in minimum counts of roughly 100 for the other three corpora used here, the BNC statistics includes $n$-grams with counts less than 10. This might be resolved by increasing the $n$-gram threshold, or simply avoiding small corpora, but for some applications it may be useful to build comprehensive FS lexicons even in relatively low resource situations. One idea we are pursing is modifying the calculation of the LPR metric to integrate uncertainty due to low counts.

There is one other more general explanation for the precision/recall imbalances we see across the four corpora: both the BNC and the Croatian corpus are composed primarily of published texts written by professional writers, particularly news. The ICWSM corpus and the Japanese corpus, on the other hand, are mostly blogs and web pages. Though all genres have FS, it is our observation that there is much more diversity in less controlled genres: many English gapped expressions, in particular, appear almost exclusively in relatively informal genres.

%The fact that less than 20\% of the FS derived from the BNC appear in the lexicon for the ICWSM corpus is fairly telling of how important genre differences are to the range of FS that will be seen in a particular corpus.

We were interested in addressing Croatian and Japanese in part because of their relatively free word order, and whether the handling of gaps would help with identifying FS in these languages. We discovered, however, that free word order actually results in \emph{more} of a tendency towards contiguous FS, not less, a fact that is reflected in our test sets (the ratio between gapped and ungapped FS) as well as the content of the lexicon. Strikingly rare in Croatian, in particular, are expressions where the content of a gap is an argument which must be filled to syntactically complete an expression: it is English whose fixed-word-order constraints often keep elements of an FS distant from each other. The gaps that do happen in Croatian are mostly prosody-driven insertions of other elements into already complete FS. This phenomena highlights a problem with the current model, in that gapped and contiguous versions of the same $n$-gram sequence (\eg \ex{take away} and \ex{take \gap away}) are, at present, considered entirely independently. Alternatives for dealing with this include collapsing statistics to create a single node in the lattice, creating a promoting link between contiguous and gapped versions of the same $n$-grams sequence in the lattice model, or switching to a dependency representation (which, we note, requires very little change to the basic model presented here, but would narrow its applicability).

As it stands, connections in the lattice are based entirely on explicit $n$-gram subsumption and overlap relations. One of the major benefits of this model as compared to alternatives is the relative ease with which additional kinds of interactions between nodes could be implemented. Another connection we have considered is based on identical or similar syntactic patterns (\eg POS sequences), which could serve to encourage the model to make generalizations: in English, \eg learning that verb-particle combinations are generally likely to be FS, whereas verb-determiner combinations are not. Our initial investigations suggest, however, it may be difficult to apply this idea without merely amplifying existing undesirable biases in the LPR measure. Bringing in other information such as simple distributional statistics might help the model identify non-compositional semantics, and could, in combination with the existing lattice competition, focus the model on detecting MWEs, which could in turn serve as a reliable basis for generalization when the raw LPR statistics alone are an unreliable indicator of formulaticity.

With respect to speed, although the optimization of the lattice is several orders of magnitude more time consuming than the decomposition heuristics of \newcite{Brooke15b}, the time needed to build and optimize the lattice was still only a fraction of the time required to collect the statistics necessary to calculate LPR, a necessary first step for both methods: therefore, the overall effect of adding the lattice optimization is fairly minimal. We note that for all four corpora, the lattice optimization algorithm converged within 10 iterations.

>>>>

\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper]{geometry}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{url}
\usepackage{xspace}
\usepackage{paralist}
\usepackage{booktabs}
\usepackage[pdftex]{graphicx}
\usepackage{algorithm,algorithmicx}
\usepackage[noend]{algpseudocode}
%\usepackage{luatexja-fontspec}
%\setmainjfont{MS Mincho} % \mcfamily
%\setsansjfont{MS Gothic} % \gtfamily
%\usepackage{xeCJK}
%\setCJKmainfont{MS Mincho} % for \rmfamily
%\setCJKsansfont{MS Gothic} % for \sffamily
\usepackage{CJKutf8}
\makeatletter
\newcommand{\@BIBLABEL}{\@emptybiblabel}
\newcommand{\@emptybiblabel}[1]{}
\makeatother
\usepackage[hidelinks]{hyperref}
\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{6.5cm}    % Expanding the titlebox

@@

\newcommand{\figref}[2][]{Figure#1~\ref{#2}\xspace}
\newcommand{\tabref}[2][]{Table#1~\ref{#2}\xspace}
\newcommand{\secref}[2][]{Section#1~\ref{#2}\xspace}
%\newcommand{\algref}[2][]{Algorithm#1~\ref{#2}\xspace}

@@

A simple but effective solution which avoids introducing extra hyperparameters is to make use of the minLPR values of the relevant nodes. In the most common two-node situation, we increase the explainedness of the cleared node based on the ratio of the minLPR of two nodes, though only if the minLPR of the lower node is higher. Generalized to the (rare) case of multiple clearing nodes, we define $\clear(t)$ as:
%in this paper, we consider two options: a hard clearing where any turned-on node will clear (set $C_{0}$ to 0 for) any node higher in the lattice which has a minLPR that is lower than it; and a soft 
\begin{displaymath}
\clear(t) = \prod_{i=1}^{m}{\min\Big(1,\frac{\minLPR(t)}{\minLPR(u_i)}\Big)}
\end{displaymath}
where $u_i$ is the $i$th clearing node of $t$, \ie turned-on nodes below $t$ in the lattice. We refer to this mechanism as ``clearing'' because it tends to clear away a variety of trivial uses of common FS which may have higher LPR due to the lexical and syntactic specificity of the FS. For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, $\clear(t)$ will be 0.5. Like \cover, \clear takes on values in the range 0 to 1, with 1 being the default when no clearing occurs. Note that one major advantage with this particular formulation of clearing is that low-LPR nodes will be unable to clear higher LPR nodes above them in the lattice; otherwise, bad FS like \ex{of the} might be selected as FS based purely to increase the explainedness of the many $n$-grams they appear in.

@@

\begin{algorithm}
	\caption{Optimization algorithm. $N$ is an ordered list of the nodes in the lattice. Nodes (designated by $n$) contain pointers to the nodes immediately linked to them in the lattice. States (designated by $s$) indicate whether each node is $ON$ or $OFF$. Explainedness values are indicated by $e$.}
	\label{alg:opt}
	\begin{algorithmic}

	\Function{LocalOpt}{$s_{start}, n, N_{rev}, N_{af\hspace{-0.1em}f}$}
		\State $s_{start} \gets \Call{Set}{s, n, ON}$
		\State $Q \gets \Call{EmptyQueue}{\null}$
		\State $e_{best} \gets 0$
		\State $s_{best} \gets NULL$
		\State \Call{Push}{Q,$s_{start}$}
		\Repeat
			\State $s_{curr} \gets \Call{Pop}{Q}$
			\State $e_{curr} \gets \Call{CalcExpl}{s_{curr}, N_{af\hspace{-0.1em}f}}$
			\For{$n_{rev} \textrm{ in } N_{rev}$}
					\State $s_{new} \gets \Call{Set}{s_{curr},n_{rev}, OFF}$
					\State $e_{new} \gets\Call{CalcExpl}{s_{new}, N_{af\hspace{-0.1em}f}}$
					\If{$ e_{new} > e_{curr}$}

					\State \Call{Push}{$Q, s_{new}$}
					\If{$e_{new} > e_{best}}$:
							\State $e_{best} \gets e_{new}$
							\State $s_{best} \gets s_{new}$
					\EndIf
					\EndIf
				\EndFor
		\Until{\Call{IsEmpty}{Q}}
	\State \Return $s_{best}$
	\EndFunction
\State
\State \Call{FrequencySortReverse}{$N$}
\State $s \gets \Call{InitializeAllOff}{N}$
\Repeat
	\State $Changed \gets FALSE$
		\For{$n \textrm{ in } N$}
		\State $N_{rev} \gets \Call{GetRelevant}{n,N}$
		\State $N_{af\hspace{-0.1em}f} \gets \Call{GetAffected}{N_{rev},N}$
		\State $s_{new} \gets \Call{LocalOpt}{s,n,N_{rev},N_{af\hspace{-0.1em}f}}$
		\If{$s_{new} \neq s$}
			\State $s \gets s_{new}$
			\State $Changed \gets TRUE$
		\EndIf
		\EndFor
\Until{$!Changed$}

@@

The dependence of the explainedness of nodes on their neighbors effectively prohibits a global optimization of the lattice. Fortunately, though most of the nodes in the lattice are part of a single connected graph, most of the effects of nodes on each other are relatively local, and effective local optimizations can be made tractable by applying some simple restrictions. The main optimization loop consists of iterations over the lattice until complete convergence (no changes in the final iteration). For each iteration over the main loop, each potentially active node is examined in order to evaluate whether its current status is optimal given the current state of the lattice. The order that we perform this has an effect on the result: among the obvious options, good results are obtained through ordering nodes by frequency, which gives an implicit advantage to relatively common $n$-grams.

Given the relationships between nodes, it is obviously not sufficient to consider switching only the present node. If, for instance, one or more of \ex{be keep \gap under wraps}, \ex{under wraps}, or \ex{be keep \gap under} has been turned on, the covering, clearing, or overlapping effects of these other nodes will likely prevent a competing node like \ex{keep \gap under wraps} from being correctly activated. Instead, the algorithm identifies a small set of ``relevant'' nodes which are the most important to the status of the node under consideration. Since turned-off nodes have no direct effect on each other, only turned-on nodes above, below, or overlapping with the current node in the lattice need be considered.  Once the relevant nodes have been identified, all nodes (including turned-off nodes) whose explainedness is affected by one or more of the relevant nodes are identified. Next, a search is carried out for the optimal configuration of the relevant nodes, starting from an `all-on' state and then iteratively considering new states with one relevant node turned off; the search continues as long as there is an improvement in explainedness. Since the node interactions are roughly cumulative in their effects, this approach will generally identify the optimal state without the need for an exhaustive search. The details of the algorithm are given as Algorithm 1.%\algref{alg:opt}.

@@

	Lattice\emph{$-$cl,ovr} & 0.47& \bf{0.53} & 0.50 & & 0.31& \bf{0.60} & 0.41 & & 0.32 & 0.66 & 0.43 & & 0.49 & 0.61 & 0.54 \\

	Lattice\emph{$-$cl} & 0.57& 0.42 & 0.49 & & 0.33& 0.58 & 0.42 & & 0.39 & 0.56 & 0.46 & & 0.63 & 0.49 & 0.55 \\

	Lattice\emph{$-$ovr} & 0.52& 0.51 & 0.51 & & 0.34& \bf{0.60} & 0.44& & 0.36 & \bf{0.67} & 0.47 & & 0.53 & \bf{0.62} & 0.58 \\

@@

The main results for FS acquisition across all four corpora are shown in \tabref{tab:main}. As noted in previous work, simple statistical association measures like PMI do fairly poorly when faced with syntactically-unrestricted $n$-grams of variable length: minLPR is clearly a much better statistic for this purpose. The LPRseg method of \newcite{Brooke15b} consistently outperforms simple ranking, and the lattice method proposed here does better still, with a margin that is fairly consistent across languages. Generally, clearing and overlap node interactions provide a relatively large increase in precision at the cost of a smaller drop in recall, though the change is fairly symmetrical in Croatian.  When only covering is used, the results are very similar to \newcite{Brooke15b}, which is unsurprising given the extent to which decomposition and covering are related. The Japanese and ICWSM corpus had relatively high precision and low recall, whereas both the BNC and Croatian corpus have low precision and high recall.

@@

 \begin{center}
 \begin{tabular}{lccccccc}
\hline
& & & & \multicolumn{4}{c}{\bf{By Length (\%) }} \\
       \cmidrule(lr){5-8}	
\bf{Lexicon} & \bf{Size} & \bf{POS types} & \bf{Gapped} (\%) & \bf{2} & \bf{3} & \bf{4}  & \bf{5+} \\ 
\hline
English ICWSM & 202k & 16.8k & 18.3 & 46.7 & 30.1 & 15.0 & 7.5  \\
English BNC & 374k &  30.0k& 26.1& 38.8 & 36.6 & 18.1 & 7.7 \\
Croatian & 172k & 6.7k & 7.9& 55.0& 31.4 & 10.3 & 3.2 \\
Japanese & 218k &  29.4k &7.9& 39.5 & 31.1& 16.8 & 12.6 \\
\hline
\end{tabular}
  \caption{Statistics for the lexicons created by our lattice method}
	 \label{tab:lexstats}

Though the results across the four corpora are reasonably similar with respect to overall F-score, there are some discrepancies. By using the standard UNIDIC morpheme representation as the base unit for Japanese, the model ends up doing an extra layer of FS identification, one which is provided by word boundaries in the other languages. The result is that there are relatively more FS for Japanese: precision is high, and recall is comparably low.  Importantly, the initial $n$-gram statistics derived from corpus actually reflect that Japanese is different: the number of $n$-gram types over length 4 is almost twice the number in the ICWSM corpus. One idea for future work is to automatically adapt to the input language/corpus in order to ensure a good balance between precision and recall.

At the opposite extreme, the low precision of the BNC is almost certainly at least somewhat a reflection of the relatively small size of the corpus: whereas the $n$-gram threshold we have used here results in minimum counts of roughly 100 for the other three corpora used here, the BNC statistics includes $n$-grams with counts less than 10. At such low counts, LPR is less reliable and more noise gets into the lexicon: the first column of \tabref{tab:lexstats} shows that the BNC is noticeably larger then the other lexicons, and the higher numbers in columns 2 and 3 (number of POS types and percentage of gapped expressions) are also indicative of increased noise.  This problem could be resolved by increasing the $n$-gram threshold. It might also make sense to simply avoid smaller corpora, though for some applications it may be useful to build comprehensive FS lexicons even in relatively low resource situations. One idea we are pursing is modifying the calculation of the LPR metric by using a more conservative estimate for probability than maximum likelihood in the case of low counts.

We were interested in addressing Croatian and Japanese in part because of their relatively free word order, and whether the handling of gaps would help with identifying FS in these languages. We discovered, however, that free word order actually results in \emph{more} of a tendency towards contiguous FS, not less, a fact that is reflected in our test sets (\tabref{tab:stats}) as well as the lexicons themselves (\tabref{tab:lexstats}). Strikingly rare in Croatian, in particular, are expressions where the content of a gap is an argument which must be filled to syntactically complete an expression: it is English whose fixed-word-order constraints often keep elements of an FS distant from each other. The gaps that do happen in Croatian are mostly prosody-driven insertions of other elements into already complete FS. This phenomena highlights a problem with the current model, in that gapped and contiguous versions of the same $n$-gram sequence (\eg \ex{take away} and \ex{take \gap away}) are, at present, considered entirely independently. Alternatives for dealing with this include collapsing statistics to create a single node in the lattice, creating a promoting link between contiguous and gapped versions of the same $n$-grams sequence in the lattice model, or switching to a dependency representation (which, we note, requires very little change to the basic model presented here, but would narrow its applicability).

The statistics in \tabref{tab:lexstats} otherwise reflect the quantity and diversity of FS across the corpora, particularly in terms of the number of POS patterns represented in the lexicon. Looking at the most common POS patterns across languages, only noun-noun and adjective-noun combinations ever account for more than 5\% of all word types in any of the lexicons. Though some of the diversity can of course be attributed to noise, it is safe to say that most FS do not fall into the standard two-word syntactic categories used in MWE work, and therefore identifying them requires a much more general approach like the one presented here.
